### 2021-07-30 doc/thesis/chapters/results.tex
re-generate

% of the entire project
asdf

>>>>

Several parts of the system design are taken into account to analyze the lines of code, to give an impression over the largest code parts in the project.

\includepicture [0.9] [0] {Lines of code of the respective system design parts, presented in a pie chart.} {lines_of_code_pie_chart} {img/matlab/lines_of_code_pie_chart_py}

%\begin{GenericCode}
%Matlab:
%  Language     files blank comment code TotalWithoutBlank Total
%  ____________ _____ _____ _______ ____ _________________ _____
%  MATLAB          34   551     728 1451              2179  2730
%
%VHDL IP Design:
%  Language     files blank comment code TotalWithoutBlank Total
%  ____________ _____ _____ _______ ____ _________________ _____
%  VHDL            20   525     787 1431              2218  2743
%  Python           1    45      22  141               163   208
%
%VHDL Testbench:
%  Language     files blank comment code TotalWithoutBlank Total
%  ____________ _____ _____ _______ ____ _________________ _____
%  Python           5   141     141  426               567   708
%  make             2    19      18   70                88   107
%  Bourne Shell     1     5       6   16                22    27
%
%HLS IP Design:
%  Language     files blank comment code TotalWithoutBlank Total
%  ____________ _____ _____ _______ ____ _________________ _____
%  C/C++ Header    14    90     119  221               340   430
%  C++              9    97     197  195               392   489
%
%HLS Testbench:
%  Language     files blank comment code TotalWithoutBlank Total
%  ____________ _____ _____ _______ ____ _________________ _____
%  C++              1    39      44  141               185   224
%  Tcl/Tk           5    33      37  112               149   182
%  C/C++ Header     2    24      18   87               105   129
%  make             1    24      26   69                95   119
%  Python           1    19      21   45                66    85
%\end{GenericCode}
